Distance Sampling in \proglang{R}

### 2016-03-18 paper.Rmd
figure 1 changes

```{r detectdists, fig.height=5.5, fig.width=9, echo=FALSE, message=FALSE, fig.cap="Top panels show an example detection function (left), the pdf of object distances (middle) and the resulting pdf of detection distances (right) for line transects. Bottom panels show an example detection function (left), the pdf of object distances (middle) and the resulting pdf of detection distances (right) for point transects. The pdf of observed detection distances in the right hand plots are obtained by multiplying the detection function by the pdf of object distances. Note, distances shown on x-axis for all plots are arbitrary. \\label{fig:detectiondist}"}

@@

set.cex  = 1
set.cex.lab = 1.2
set.cex.main = 2
#Line transect example
plot(x, y, xlab = "Perpendicular distance", ylab = "Probability of detection", type = "l", ylim = c(0,1.1), cex = set.cex, cex.lab = set.cex.lab)
line.availability <- rep(1,100)
plot(x, line.availability, xlab = "Perpendicular distance", ylab = "pdf of object distances", type = "l", ylim = c(0,1.1), xlim = c(0,500), yaxt = "n", cex = set.cex, cex.lab = set.cex.lab, main = "Line Transect", cex.main = set.cex.main)
plot(x,y, xlab = "Perpendicular distance", ylab= "pdf of observed distances", type = "l", ylim = c(0,1.1), yaxt = "n", cex = set.cex, cex.lab = set.cex.lab)

#Point Transect example
plot(x, y, xlab = "Radial distance", ylab = "Probability of detection", type = "l", ylim = c(0,1.1), cex = set.cex, cex.lab = set.cex.lab)
point.availability <- 2*pi*x
plot(x, point.availability, xlab = "Radial distance", ylab = "pdf of object distances", type = "l", ylim = c(0,3300), xlim = c(0,500), yaxt = "n", cex = set.cex, cex.lab = set.cex.lab, main = "Point Transect", cex.main = set.cex.main)
point.observed <- y*point.availability
plot(x, point.observed, xlab = "Radial distance", ylab= "pdf of observed distances", type = "l", ylim = c(0,800), yaxt = "n", cex = set.cex, cex.lab = set.cex.lab)

>>>>

```{r detectdists, fig.height=5.5, fig.width=9, echo=FALSE, message=FALSE, fig.cap="Panels show an example detection function (left), the pdf of object distances (middle) and the resulting pdf of detection distances (right) for line transects (top row) and point transects (bottom row). The pdf of observed detection distances in the right hand plots are obtained by multiplying the detection function by the pdf of object distances and rescaling. In this example, detection probability becomes effectively zero at 500 (distances shown on $x$-axis are arbitrary). \\label{fig:detectiondist}"}

@@

set.cex  = 1
set.cex.lab = 1.2
set.cex.main = 2
#Line transect example
plot(x, y, xlab = "Perpendicular distance", ylab = "Probability of detection", type = "l", ylim = c(0,1.1), cex = set.cex, cex.lab = set.cex.lab)
line.availability <- rep(1,100)
plot(x, line.availability, xlab = "Perpendicular distance", ylab = "pdf of object distances", type = "l", ylim = c(0,1.1), xlim = c(0,500), cex = set.cex, cex.lab = set.cex.lab, main = "Line Transect", cex.main = set.cex.main)
plot(x,y, xlab = "Perpendicular distance", ylab= "pdf of observed distances", type = "l", ylim = c(0,1.1), cex = set.cex, cex.lab = set.cex.lab)

#Point Transect example
plot(x, y, xlab = "Radial distance", ylab = "Probability of detection", type = "l", ylim = c(0,1.1), cex = set.cex, cex.lab = set.cex.lab)
point.availability <- 2*pi*x
plot(x, point.availability, xlab = "Radial distance", ylab = "pdf of object distances", type = "l", ylim = c(0,3300), xlim = c(0,500), cex = set.cex, cex.lab = set.cex.lab, main = "Point Transect", cex.main = set.cex.main)
point.observed <- y*point.availability
plot(x, point.observed, xlab = "Radial distance", ylab= "pdf of observed distances", type = "l", ylim = c(0,800), cex = set.cex, cex.lab = set.cex.lab)
